---
title: "swirlpractice"
author: "Wade Dennis"
date: "2026-04-13"
output: html_document
---
\
exercise 1:  
\
```{r}
library(tidyverse)
temp <- 2000:20000
sum(temp)
```
\
exercise 2:  
\
```{r}
a <- 5
b <- 2:20
a
b
```
The above code made 2 objects a and b which were first instantiated with the number 5 in the first case and numbers 2 through 20 in the second case.   
Next, then their values were displayed in lines 3 and 4.  
\
exercise 3:  
\
```{r}
c <- a + b
d <- sum(a,b)
test <- sum(b)+5
test2 <- b + a
c
d
test
test2
```
As we can see, sum() will sum what is inside the brackets, while the + while keep the object as a list of numbers with each element added by 5.  
\
exercise 4:  
\
```{r}
sum(b[5:10])
```
\
exercise 5:  
\
```{r}
sum(b[c(3, 8, 10)])
```
\
__2 Dimensional Objects:__  
\
exercise 6:  
\
```{r}
m <- matrix(data=1:25,ncol=5,byrow=T)
m
m[5,5]
#ny code below
m[3,]
mymatrix <- bind_cols(m[,3],m[,3],m[,5])
mymatrix
```
The first number specifies row and the second number specifies column.  
m[3,] will get the entire 3rd row of a table.  
\
exercise 7:
\
```{r}
cbind(m,101:105)
```
cbind() adds a column on to a given dataframe and takes the df as first argument and the column itself as the second argument (top to bottom).  
\
exercise 8:  
\
I took a week break between doing the practice and this, and I have somehow lost my notes I took. sorry!
